Reply to Reviewer #1

### 2022-02-07 Codes/PrepareResults.rmd
made significant modifications to the manuscript and response to reviewers

knitr::opts_chunk$set(
  cache = TRUE,
  warning = FALSE,
  message = FALSE
)
```

```{r packages, cache = FALSE, include = FALSE}
# === packages ===#
# --- data wrangling--- #
library(sf)
library(data.table)
library(tidyverse)

@@

library(causalTree)
library(here)
library(rpart)
library(rattle)

@@

```{r}
source("./GitControlled/Codes/0_1_functions_gen_analysis_data.R")

pCorn <- price_table[2, pCorn]
pN <- price_table[2, pN]

# /*=================================================*/
#' # Field Data Sets
# /*=================================================*/

# /*----------------------------------*/
#' ## (1) cell-level data set
# /*----------------------------------*/
# + NOTE: I needed to do the following things, because the existing raw data does not have m_error
field <- readRDS(here("Shared/Data/for_Simulations/field_padding.rds"))

coef_data <- readRDS(here("Shared/Data/for_Simulations/coefficients_sprange_400.rds"))

x <- 1
coef_data_m <- coef_data[sim == x, ]
coef_data_t <- coef_data[sim == ifelse(x + 1 >= max(sim), 1, x + 1), ]

sample_dt_cell <- prepare_raw_data(x, field = field, coef_data_m = coef_data_m, coef_data_t = coef_data_t, app_error = "no") %>%
  .$reg_raw_data

field_cell_sf <-
  left_join(select(field, unique_cell_id), field_cell_dt, by = "unique_cell_id") %>%
  na.omit() %>%
  mutate(plot_id = ceiling(subplot_id / 4)) %>%
  filter(padding == 1)

saveRDS(field_cell_sf, here("Shared/Results/for_writing/sample_field_cell_sf.rds"))

# /*----------------------------------*/
#' ## (2) subplot-level field without padding area
# /*----------------------------------*/

field_subplot_sf <-
  field_cell_sf %>%
  group_by(subplot_id, strip_id) %>%
  summarise(
    sim = mean(sim),
    yield = mean(yield),
    opt_N = mean(opt_N),
    rate = mean(rate),
    aa_n = mean(aa_n),
    alpha = mean(alpha),
    beta = mean(beta),
    ymax = mean(ymax),
    alpha1 = mean(alpha1),
    alpha2 = mean(alpha2),
    beta1 = mean(beta1),
    beta2 = mean(beta2),
    ymax1 = mean(ymax1),
    ymax2 = mean(ymax2),
    theta_1 = mean(theta_1),
    theta_2 = mean(theta_2)
  ) %>%
  mutate(unique_subplot_id = paste0(strip_id, "_", subplot_id)) %>%
  select(!c(strip_id, subplot_id))

saveRDS(field_subplot_sf, here("Shared/Results/for_writing/sample_field_subplot_sf.rds"))
```

>>>>

knitr::opts_chunk$set(
  cache = TRUE
)
```
```{r packages, cache = FALSE, include = FALSE}
# === packages ===#
# --- data wrangling--- #
library(sf)
library(data.table)
library(tidyverse)

@@

@@

### 2022-02-07 Writing/CEA_2nd_round/replies_rev_1.rmd
made significant modifications to the manuscript and response to reviewers

The core objective of the paper is to test the CF against existing ML methods in predicting EOIR and economic performance of resulting site-specific input use recommendations. To this core objective, ML simulations are our core method. For this reason, in our Materials and Methods section, we would like to avoid the explanation of how CF works just like we do not give much explanations to any of RF, BRF, and CNN, which are well-established and mostly understood already by the readers of this journal. However, since this article is the first to apply CF in the field of agronomy, let alone site-specific input management, we believe that it is worthwhile to present how it works in detail and what conditions are necessary for it to work well. Now, if we place such description inside the Materials and Method section, it will break the flow of explaning how MC simulations work, temporarily distracting readers from how MC simulations are conducted to the details of how CF works. Instead of this, we believe that it is beneficial to first give readers knowledge on how CF works and the potential advantages over the existing predition-oriented ML methods as essential knowledge before we move onto how our MC simulations are conducted in the Materials and Method section, in which we would like to focus on how MC simulations are conducted. Therefore, we kept 2.3 and 2.4 in the current manuscript.

We talk about identifying site-specific economically optimal input rates in three different places. However, each of them serves distinctive purposes and we would like to keep the current structure if that is acceptable to you.

Section 2.1: bluh bluh
Section 3.: true optimal N
Section 3.: estiamted optimal N

@@

<span style="color:blue">  
We first apologogize that misleading section and subsection titles may have caused confusions about your perceived structural redundancy of this article.

We wrote the initial manuscript with avoiding redundancy in mind and we beleived that we did not have any redundancy in our paper. Therefore, we struggled tremendously to see where the redundancies are. We would really appreciate it if you could specify where you see redundancies and why so that we can address prorperly.

In MC simulation studies, we believe that presenting how data is generated in detail is crucial because the results are dependent on how data is generated. It is much like any emprical studies using real experiment data provides lots of details about the experiemnts. We take reproducibility seriously and we believe that the details we peovided in our manuscript is appropriate. Therefore, we had very hard time telling which is unnecessary and not. We would really appreciate it if you could specify which parts are not critical.

@@

+ I provided the unit in the text. It is degree.

@@

+ I added the explanation for those numbers as a footnote in the figure. 
</span>

**6. Some formulas in the manuscript are not numbered (lines 116, 120, 268, 291, 371, 389).**
<span style="color:blue">

+ I numbered all the formulas. 
</span>

@@

+ I modified this sentence "For each simulated field, we generated a training data set and a validation data set." For each simulation round, one of the fields was used as a training data set, and another field that is different from the one used as a training data set in that round was used as a validation data set.

@@

**8. I can’t open the code link (https://github.com/tmieno2/ML_VRA.git, lines 199 and 249) with my browsers (chrome, edge, and Firefox). Please upload the code to the public research data repositories (Zenodo, Mendeley Data, figshare, Harvard Dataverse, etc.), not GitHub. Please generate a separate DOI for your code and cite it.**
<span style="color:blue">  
+ I uploaded to the simulation codes and the data on Mendeley Data. The link is suggested on section 3: Materials and Methods.

@@

+ I converted to those units to meter (m)

@@

+ I updated Figure 2. The number of rows and columns of plots, subplots, and cells schematics are indicated each map in Figure 2.
</span>

**11. The titles of sections 3.2.1 and 3.2.2 do not provide useful information to the readers, please revise the titles. (lines 342 and 373)**
<span style="color:blue">

+ I changed the title of section 3.2 to "Training Models and Estimating Site-specific EONRs". Further, I revised the title of sections 3.2.1 and 3.2.2 to "Estimation of site-specific EONRs by RF, BRF, and CNN" and "Estimation of site-specific EONRs by CF", respectively. 
</span>

@@

+ I changed the title of section 4.2 to "The relationships between yield prediction performance and EONR prediction performance". 
</span>

@@

**15. Please add a separate section for research gaps or uncertainties. Are there any prerequisite assumptions for using the CF model?**
<span style="color:blue">

>>>>

We have moved an example of causal tree (previously in seciton 2.3), but decide to keep the explanation of how CF works. The core objective of the paper is to test the CF against existing ML methods in predicting EOIR and economic performance of resulting site-specific input use recommendations. To this core objective, ML simulations are our core method. For this reason, in our Materials and Methods section, we would like to avoid the explanation of how CF works just like we do not give much explanations to any of RF, BRF, and CNN, which are well-established and mostly understood already by the readers of this journal. However, since this article is the first to apply CF in the field of agronomy, let alone site-specific input management, we believe that it is worthwhile to present how it works in detail and what conditions are necessary for it to work well. Now, if we place such description inside the Materials and Method section, it will break the flow of explaning how MC simulations work, temporarily distracting readers from how MC simulations are conducted to the details of how CF works. Instead of this, we believe that it is beneficial to first give readers knowledge on how CF works and the potential advantages over the existing predition-oriented ML methods as essential knowledge before we move onto how our MC simulations are conducted in the Materials and Method section, in which we would like to focus on how MC simulations are conducted. Therefore, we kept 2.3 and 2.4 in the current manuscript.

@@

In rereponse to this comments, we made several changes.

First, we consolidated 3.1.2 and 3.1.3 in the previous round into a single subsubsection called "Cell-specific Yield Functions and True Economically Optimal N Rates." In doing so, we dropped detailed explanation of the conceptual framework behind the yield response functions based on cell-leve characteristics, $c_i$, and moved it to the supplemnentary appendix (Appendix B). We also removed our detailed description of how parameters and error term were generated and moved it to Appendix C along with relevant tables and figures (spefically table x and figures x, y, z) <span style = "color: blue;"> Shun put table and figure numbers here </span>.

Second, we consolidated 3.1.4 and 3.1.5 in the previous round into a single subsubsection called "Trial Design and Yield Data Generation for Modeling." In doing so, we cut some texts and combined figure x and y in the previous round into a single figure (figure x in the current manuscript).

Third, we removed detailed description of how some parameters are splitted into two parts and moved it to the Appendix.

In MC simulation studies, we believe that presenting how data is generated in detail is crucial because the results are dependent on how data is generated. It is much like any emprical studies using real experiment data provides lots of details about the experiemnts. We take reproducibility seriously and we believe that the details we peovided in our current manuscript is appropriate and it is hard for us to further slim down the section. Moreover, we believe we no longer have any redundancy in this section any more.

@@

It is degree. The unit is now provided in Appendix A.

@@

The explanation for those numbers are added as a footnote to the figure (Figure <span style = "color: blue;"> Shun, figure number </span>). 
</span>

**6. Some formulas in the manuscript are not numbered (lines 116, 120, 268, 291, 371, 389).**

<span style="color:blue">  
All the formulas are now numbered. 
</span>

@@

We aplogogize that we are not clear on this respect.

Trainign dataset and test dataset are completely separate. Models are trained on the entirety of the train data for each simulation, and then the trained model is tested against a test dataset that are different in the underdyling field parameters $\alphe$, $\beta$, and $ymax$. The train dataset, however, was split into several parts when cross-validation was performed in determing the optimal hyperparameters at each simulation round.

We added the following paragraph to section <span style = "color: blue;"> Shun section number here </span> to make this point clear.

"For evaluation of yield and EONR predictions, a dataset from a different simulation round was used as the test dataset. For example, for simulation number 1, train dataset from simulation number 2 was used as the test dataset. This process works because the train datasets were generated by the same data generating process, yet have different underlying field parameters ($\alpha$, $\beta$, $ymax$). Furtehr, each of the "train" datasets are generated independet of one another. Thefore, for a particular simulation round, the dataset in any of the other simualtions can serve as a valid test dataset. This practice avoid creating another set of 1000 simulations fields unnecessarily."

@@

**8. I can’t open the code link (https://github.com/tmieno2/ML_VRA.git, lines 199 and 249) with my browsers (chrome, edge, and Firefox). Please upload the code to the public research data repositories (Zenodo, Mendeley Data, figshare, Harvard Dataverse, etc.), not GitHub. Please generate a separate DOI for your code and cite it.**

<span style="color:blue">  
We realized that the github repository was private and that was why you were not able to access it. We made a public github repository named CF_for_VRA ([here](https://github.com/tmieno2/CF_for_VRA)).

The simulation codes and the data were also shared on Mendeley Data (<span style = "color: blue;"> Shun, provide the link here </span>) according to the Editor's suggestion for the ease of access. The link is also provided <span style = "color: blue;"> Shun, be speficic about where it is </span>.

@@

All the lenth units were converted to meter (m)

@@

The number of rows and columns of plots, subplots, and cells schematics are now indicated Figure 2.
</span>

**11. The titles of sections 3.2.1 and 3.2.2 do not provide useful information to the readers, please revise the titles. (lines 342 and 373)**

<span style="color:blue">  
We realized that section 3.1 has also a bad title. Therefore, we changed it to "Training Models and Estimating Site-specific EONRs". Further, the title of sections 3.2.1 and 3.2.2 were changed to "Estimation of site-specific EONRs by RF, BRF, and CNN" and "Estimation of site-specific EONRs by CF", respectively. 
</span>

@@

The title of 4.1 was changed to "Comparison of EONR estimation accuracy" to reflect its contents. The title of section 4.2 was changed to "The relationship between yield and EONR prediction performances". 
</span>

@@

**15. Please add a separate section for research gaps or uncertainties. Are there any prerequisite assumptions for using the CF model?**
